An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-26 1_intro.tex
title: system => framework

There is a large body of literature on relating process parameters such as bead width to various mechanical properties of the end part.
The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads. \cite{N.Turner2014,ahn2002anisotropic}
In order to accurately fabricate a part restricted to prescribed mechanical properties, we need to generate toolpaths using the corresponding process parameters as close as possible.
We therefore develop a parametric system which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the nominal bead width compared to existing techniques.
See \cref{intro_wedge}(bottom).

>>>>

There is a large body of literature on relating process parameters such as bead width to various mechanical properties of the end part.
The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads. \cite{N.Turner2014,ahn2002anisotropic}
In order to accurately fabricate a part restricted to prescribed mechanical properties, we need to generate toolpaths using the corresponding process parameters as close as possible.
We therefore develop a framework which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the nominal bead width compared to existing techniques.
See \cref{intro_wedge}(bottom).
